Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-06-15 ms.tex
updated notes and apertures for OTIS illum grism time series test

A series of NIRCam stability tests were carried out while the entire JWST telescope system was placed in a tall vacuum chamber at NASA Johnson.
However, there is no feasible way to place a point source lamp at infinity to simulate the imaging of astrophysical objects onto a JWST instrument, so an alternate lamp setup is used.
During these tests, there were two configurations 1) the ``half pass" tests where lamp sources within the optical system and 2) ``pass and a half" tests where the a lamp source within the optical system bounces light off the secondary, primary, flat mirrors mounted on the chamber's ceiling and then through the entire telescope and instrument chain.

The OTIS testing included a time series mode similar to the grism time series template used in orbit for transiting planets.
Figure \ref{fig:otisPSFs} shows the point spread functions for the OTIS tests that simultaneously illuminated the short wavelength and long wavelength channels.
The ``O9'' supercontinuum illuminated the detector over a wide wavelength range from 2.5 to 4.1$\mu$m.
A small fraction of the light is emitted at wavelengths shorter than 2.5 $\mu$m, which is sufficient to illuminate the short wavelength detector to peak counts of $\sim 260$DN per exposure.
Meanwhile, the peak of the grism is $\sim$ 26,000 DN.
This lamp configuration was a pass and a half test, which suffered from the vibrations and oscillations of the suspension system, which can be perturbed by motors such as vacuum pumps.

@@

>>>>

A series of NIRCam stability tests were carried out while the entire JWST telescope system was placed in a tall vacuum chamber at NASA Johnson.
However, there is no feasible way to place a point source lamp at infinity to simulate the imaging of astrophysical objects onto a JWST instrument, so an alternate lamp setup is used.
During these tests, there were two configurations 1) the ``half pass" tests where lamp sources within the optical system and 2) ``pass and a half" tests where the a lamp source within the optical system bounces light off the secondary, primary, flat mirrors mounted on the chamber's ceiling and then through the entire telescope and instrument chain to the detectors.

\subsubsection{Pass and a Half Grism Time Series Test}
The OTIS testing included a time series mode similar to the grism time series template used in orbit for transiting planets.
Figure \ref{fig:otisPSFs} shows the point spread functions for the OTIS tests that simultaneously illuminated the short wavelength and long wavelength channels.
The ``O9'' supercontinuum illuminated the detector over a wide wavelength range from 2.5 to 4.1$\mu$m.
A small fraction of the light is emitted at wavelengths shorter than 2.5 $\mu$m, which is sufficient to illuminate the short wavelength detector to peak counts of $\sim 260$DN per exposure.
Meanwhile, the peak of the grism is $\sim$ 26,000 DN.
This lamp configuration was a pass and a half test, which suffered from the vibrations and oscillations of the suspension system, which can be perturbed by motors such as vacuum pumps.
The telescope is suspended vertically and can potentially swing under these vibrations.

@@

\subsubsection{Half Pass Subarray Size Tests}
